---
title: "Earthquake Capacity-Spectrum Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Earthquake Capacity-Spectrum Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(hazgrid)
library(terra)
ext <- function(...) system.file("extdata", ..., package = "hazgrid")
```

The earthquake workflow is being upgraded toward the Hazus capacity-spectrum
method. It requires validated lookup tables for real analysis. The current
implementation uses an elastic-demand intersection; full effective-damping
iteration remains under development.

Typed lookup-table templates are installed under `inst/extdata/schemas/`.
Populate them from official FEMA Hazus or independently validated sources.

```{r earthquake, eval=FALSE}
result <- run_earthquake_loss(
  inventory = "path/to/inventory.gpkg",
  pga = rast("path/to/pga.tif"),
  sa03 = rast("path/to/sa03.tif"),
  sa10 = rast("path/to/sa10.tif"),
  capacity_table = "path/to/validated_capacity_curve.csv",
  structural_fragility_table = "path/to/validated_structural_fragility.csv"
)
```

The demand-spectrum stage is independently inspectable:

```{r spectrum}
spectrum <- build_demand_spectrum(pga = 0.2, sa03 = 0.5, sa10 = 0.25)
head(spectrum)
```
