---
title: "Tsunami Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tsunami Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(hazgrid)
library(terra)
ext <- function(...) system.file("extdata", ..., package = "hazgrid")
```

`hazgrid` separates tsunami hazard preparation, hazard extraction, damage
probabilities, casualties, expected economic loss, assumptions, and lookup
validation. Real analyses require official FEMA Hazus or independently
validated lookup tables.

Typed schema templates are installed under `inst/extdata/schemas/`. Populate
them from official FEMA Hazus sources or independently validated tables before
running a real analysis.

## Level 2: Depth and velocity

```{r level2, eval=FALSE}
result <- run_tsunami_loss(
  inventory = "path/to/inventory.gpkg",
  depth = rast("path/to/depth.tif"),
  velocity = rast("path/to/velocity.tif"),
  fragility_table = "path/to/validated_tsunami_fragility.csv",
  loss_ratio_table = "path/to/validated_tsunami_loss_ratio.csv"
)
```

## Level 3: Depth and momentum flux

```{r level3, eval=FALSE}
result <- run_tsunami_loss(
  inventory = "path/to/inventory.gpkg",
  depth = rast("path/to/depth.tif"),
  momentum_flux = rast("path/to/momentum_flux.tif"),
  fragility_table = "path/to/validated_tsunami_fragility.csv",
  loss_ratio_table = "path/to/validated_tsunami_loss_ratio.csv"
)
```

The structural layer is `HV2`. Nonstructural, contents, and casualty methods
use `H`. Use `read_hazgrid_lookup()` to load validated tables for real analyses.
