---
title: "Tsunami Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tsunami Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(hazgrid)
library(terra)
ext <- function(filename) system.file("extdata", filename, package = "hazgrid")
```

`hazgrid` separates tsunami hazard preparation, hazard extraction, damage
probabilities, and expected economic loss. The bundled lookup tables use
invented demonstration values and must not be treated as official Hazus values.

## Level 2: Depth and velocity

```{r level2}
inventory <- read_inventory(ext("synthetic_buildings.gpkg"))
depth <- rast(ext("synthetic_depth.tif"))
velocity <- rast(ext("synthetic_velocity.tif"))

hazard_l2 <- prepare_tsunami_hazard(depth, velocity = velocity)
exposure_l2 <- extract_hazard(hazard_l2, inventory)
damage_l2 <- tsunami_damage(exposure_l2, ext("tsunami_fragility_example.csv"))
loss_l2 <- tsunami_economic_loss(damage_l2, ext("tsunami_loss_ratios_example.csv"))
summarize_by(loss_l2, "municipality")
```

## Level 3: Depth and momentum flux

```{r level3}
flux <- compute_tsunami_momentum_flux(depth, velocity)
hazard_l3 <- prepare_tsunami_hazard(depth, momentum_flux = flux)
names(hazard_l3)
```

The structural layer is `HV2`. Nonstructural, contents, and the casualty MVP
use `H`. `tsunami_casualty_mvp()` is intentionally a replaceable placeholder,
not the complete Hazus casualty model.
